Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2022-03-07 reportTII-ArticleHIL.tex
Update report
I added some text to the main project work section of the report.

Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually. This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in. After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models. When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor. As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode. For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems. For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.

>>>>

Using the data we collected for the steering, acceleration, and braking subsystems, we initially separated the data so we could analyze the by-wire and manual modes individually. This effort was made to identify if the models we developed could be used interchangeably regardless of what mode the autonomous vehicle subsystems were operating in. After analyzing the models we developed, we determined that they are not interchangeable as there were differences in the models. When the vehicle subsystem is in by-wire mode, the controller AutonomouStuff developed is generating the torque voltages that are applied to each subsystem motor. As a result, we decided the most accurate model of each subsystem would be developed using the data when the subsystems are in manual mode. For reference, the differences in the models created for by-wire and manual mode are depicted in \ref{sec:simresults} for the steering and acceleration subsystems. For all other models we develop, we will only use manual mode data and will not create models for by-wire mode.
\\

Another decision we made was to start using the Neural Network to create models. We decided to do this instead of continuing with the System Identification Toolbox for multiple reasons. The main one is because while transfer function models are able to accurately model linear systems, they struggle to model highly non-linear systems. Neural Networks work well with highly non-linear systems and are able to accurately model them. Since our systems, and the steering system in particular, exhibit non-linear behavior, they are not able to be accurately modeled by transfer functions. Another reason is that once the System Identification models were created in Simulink, there was confusion over how they would connect to produce the output. Some of the system models, such as the brake system, had four transfer functions due to having four inputs. These models were easily generated, but it wasn’t clear on how they should be connected in order to reflect the physical system. By using Neural Network models this problem can be avoided.
